UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-07-09 ms/main.tex
figure legends

\subsubsection*{Acknowledgements}
We thank all participants in the HRS, UKBB, and 1KGP for providing their genetic data as well as the teams who generated and assembled the datasets. We also thank Jose Sergio Hleap, Mark Lathrop, Dominic Nelson, Markus Munter, Stephen Sawcer, and Audrey Grant for useful discussions about science, programming, and data access; David Poznik, Liz Babalola, and Adam Auton from 23andMe for discussing findings in the 1KGP; and Selin Jessa for introducing us to UMAP. This research has been conducted using the UK Biobank Resource under Application Number 6728.

@@

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=0.75\textwidth]{images/HRS_1000G_NP1_UMAP_PC10_NC2_NN15_MD05_pca_1kgp_onto_hrs_umap_1kgp_onto_hrs_2018112221116_born.pdf}
    \end{subfigure}
    \caption{UMAP on the top 10 principal components of the HRS dataset, coloured by Census Bureau birth region. Each colour represents one of the 10 birth regions. There is no obvious pattern in the clusters of majority "White Not Hispanic" individuals.}
    \label{fig:supp_hrs_born}
\end{figure*}

>>>>

\subsubsection*{Acknowledgements}
We thank all participants in the HRS, UKBB, and 1KGP for providing their genetic data as well as the teams who generated and assembled the datasets. We also thank Audrey Grant, Ryan Hernandez, Jose Sergio Hleap, Mark Lathrop, Dominic Nelson, Markus Munter, Stephen Sawcer, Melissa Spear, and Dara Torgerson for useful discussions about science, programming, and data access; David Poznik, Liz Babalola, and Adam Auton from 23andMe for discussing findings in the 1KGP; and Selin Jessa for introducing us to UMAP. This research has been conducted using the UK Biobank Resource under Application Number 6728.

@@

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=0.9\textwidth]{images/HRS_1000G_NP1_UMAP_PC10_NC2_NN15_MD05_pca_1kgp_onto_hrs_umap_1kgp_onto_hrs_2018112221116_born.jpeg}
    \end{subfigure}
    \caption{UMAP on the top 10 principal components of the HRS dataset, coloured by Census Bureau birth region. Each colour represents one of the 10 birth regions. There is no obvious pattern in the clusters of majority "White Not Hispanic" individuals.}
    \label{fig:supp_hrs_born}
\end{figure*}
